Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip \LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par

### 2022-01-23 paper.tex
(paper) citations and add coauthor

% Created 2022-01-23 Sun 15:00
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:orgd2a88f9}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent (\citeprocitem{9}{NCHIT, 2021}). Increasingly, this data helps address 4 challenges associated with healthcare:

@@

At the same time, healthcare consumers are making more decisions and have to navigate an increasingly complex system. Traditionally, diagnosing a patient’s condition has been based heavily on the umbrella approach, which is based solely on the patient-reported symptoms, resulting in an umbrella diagnosis and treatment that frequently fails to achieve their intended effects due to individual variability. As a result, many existing therapies fail to achieve their intended effects due to individual variability. Precision medicine aims to allow tailor prevention and treatment with an individual approach. (\citeprocitem{11}{Ravizza et al., 2019}). Due to the complexity of human biology, individualized medicine requires taking into account aspects that go well beyond standard medical care. Medical care only has a relative contribution of 10 to 20 percent to outcomes; health-related behaviors, socioeconomic factors, and environmental aspects account for the other 80 to 90 percent (\citeprocitem{6}{Magnan \& , 2017}). Computationally, the interdependencies and correlations among these diverse contributors create formidable challenges concerning optimizing treatment effectiveness. (\citeprocitem{7}{McDermott et al., 2012})

@@

\section{AI in Precision Medicine}
\label{sec:orgcac6fb6}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org57976b0}

Quantum computers process information in a fundamentally different way from traditional computers. Previous computer technology advancements—such as integrated circuits—enabled faster computing, but were still based on classical information processing. These computers manipulate quantum bits (qubits). These are unlike classical bits, which store information as either a 0 or 1, and they can display uniquely quantum properties, such as entanglement. As a result, it becomes possible to construct quantum algorithms that can outperform their classical counterparts which are not able to leverage quantum phenomena. (\citeprocitem{8}{Montanaro, 2016})

\begin{itemize}
\item Chemistry, machine learning/artificial intelligence (AI), optimization, or simulation tasks. Machine learning has shown potential to be enhanced by quantum computing and is symbiotically helping drive quantum advances (\citeprocitem{2}{Carleo \& Troyer, 2017})
\item Complex correlations and interdependencies among many highly interconnected elements, such as molecular structures in which many electrons interact
\item Inherent scaling limits of relevant classical algorithms. For instance, the resource requirements of classical algorithms may increase exponentially with problem size, as is the case when simulating the time evolution of quantum systems (\citeprocitem{12}{Whitfield et al., 2011}).
\end{itemize}

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:orgaad1700}

@@

The most computationally demanding part of gradient-based algorithms, namely, computing the fitness function and its gradient for control input, can be accomplished by the process of evolution and measurement on quantum hardware. By posing queries to and receiving answers from these devices, classical computing devices update the control parameters until an optimal control solution is found.

Using this hybrid approach gives rise to interesting areas of research that seek to leverage the principles of quantum mechanics to augment machine learning or vice-versa. Enabling us to enhance classical ML algorithms by outsourcing difficult calculations to a quantum computer.

@@

\subsection{Generative Adversarial Networks}
\label{sec:org8f70103}

Generative Adversarial Networks, or GANs for short, are an approach to generative modeling using deep learning methods, such as convolutional neural networks. Generative modeling is an unsupervised learning task in machine learning that involves automatically discovering and learning the regularities or patterns in input data in such a way that the model can be used to generate or output new examples that plausibly could have been drawn from the original dataset.

@@

\subsubsection{MolGAN}
\label{sec:orgce38a3d}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:orgac8eb1e}

@@

\section{Prototype}
\label{sec:org2ab3ce7}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:orgeed551a}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:org15b0e26}

@@

\subsection{Data}
\label{sec:orgc7a20ea}

@@

\subsection{Tools and Hardware}
\label{sec:org7764740}

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer (\citeprocitem{10}{Quantum, 2021})

@@

\section{Results}
\label{sec:orgf7b059b}

\subsection{Speed}
\label{sec:orgd3deb47}

@@

\subsection{Accuracy}
\label{sec:org2aa665c}

@@

\subsection{Pricing}
\label{sec:orgf3f3cb9}

@@

\section{Conclusion and Further Research}
\label{sec:org41345ee}

@@

\section{References}
\label{sec:org3c7375e}

@@

\hypertarget{citeproc_bib_item_6}{Magnan, S., \& . (2017). Social determinants of health 101 for health care: Five plus five. \textit{NAM Perspectives}, \textit{7}(10). \url{https://doi.org/10.31478/201710c}}

\hypertarget{citeproc_bib_item_7}{McDermott, J. E., Wang, J., Mitchell, H., Webb-Robertson, B.-J., Hafen, R., Ramey, J., \& Rodland, K. D. (2012). Challenges in biomarker discovery: combining expert insights with statistical analysis of complex omics data. \textit{Expert Opinion on Medical Diagnostics}, \textit{7}(1), 37–51. \url{https://doi.org/10.1517/17530059.2012.718329}}

\hypertarget{citeproc_bib_item_8}{Montanaro, A. (2016). Quantum algorithms: an overview. \textit{Npj Quantum Information}, \textit{2}(1). \url{https://doi.org/10.1038/npjqi.2015.23}}

\hypertarget{citeproc_bib_item_9}{NCHIT. (2021). \textit{Non-federal acute care hospital electronic health record adoption}. \url{https://www.healthit.gov/data/quickstats/non-federal-acute-care-hospital-electronic-health-record-adoption}}

\hypertarget{citeproc_bib_item_10}{Quantum, I. (2021). \textit{Ibm quantum services}. \url{https://quantum-computing.ibm.com/}}

\hypertarget{citeproc_bib_item_11}{Ravizza, S., Huschto, T., Adamov, A., Böhm, L., Büsser, A., Flöther, F. F., Hinzmann, R., König, H., McAhren, S. M., Robertson, D. H., Schleyer, T., Schneidinger, B., \& Petrich, W. (2019). Predicting the early risk of chronic kidney disease in patients with diabetes using real-world data. \textit{Nature Medicine}, \textit{25}(1), 57–59. \url{https://doi.org/10.1038/s41591-018-0239-8}}

\hypertarget{citeproc_bib_item_12}{Whitfield, J. D., Biamonte, J., \& Aspuru-Guzik, A. (2011). Simulation of electronic structure hamiltonians using quantum computers. \textit{Molecular Physics}, \textit{109}(5), 735–750. \url{https://doi.org/10.1080/00268976.2011.552441}}
\end{hangparas}

>>>>

% Created 2022-01-23 Sun 15:10
% Intended LaTeX compiler: pdflatex
\documentclass{scrartcl}
\renewcommand\sectionformat{\llap{\thesection\autodot\enskip}}
\renewcommand\subsectionformat{\llap{\thesubsection\autodot\enskip}}
\renewcommand\subsubsectionformat{\llap{\thesubsubsection\autodot\enskip}}

@@

\author{Shaurya Singh, Abrahim Mahmud}
\date{\today}
\title{Accelerating Precision Medicine with Quantum Computing and AI\\\bigskip
\LARGE\mdseries\itshape\color{black!80} Exploring the future of Personalized Health Care\par}
\colorlet{greenyblue}{blue!70!green}
\colorlet{blueygreen}{blue!40!green}
\providecolor{link}{named}{greenyblue}
\providecolor{cite}{named}{blueygreen}
\hypersetup{
  pdfauthor={Shaurya Singh, Abrahim Mahmud},
  pdftitle={Accelerating Precision Medicine with Quantum Computing and AI},
  pdfkeywords={},
  pdfsubject={},
  pdfcreator={Emacs 29.0.50 (Org mode 9.6)},
  pdflang={English},
  breaklinks=true,
  colorlinks=true,
  linkcolor=,
  urlcolor=link,
  citecolor=cite
}
\urlstyle{same}
\makeatletter
\newcommand{\citeprocitem}[2]{\hyper@linkstart{cite}{citeproc_bib_item_#1}#2\hyper@linkend}
\makeatother

@@

\section{Introduction}
\label{sec:org94b9d88}

Healthcare data—such as information from clinical trials, disease registries, electronic health records (EHRs), and medical devices—is growing at a compound annual growth rate of 36 percent (\citeprocitem{10}{NCHIT, 2021}). Increasingly, this data helps address 4 challenges associated with healthcare:

@@

At the same time, healthcare consumers are making more decisions and have to navigate an increasingly complex system. Traditionally, diagnosing a patient’s condition has been based heavily on the umbrella approach, which is based solely on the patient-reported symptoms, resulting in an umbrella diagnosis and treatment that frequently fails to achieve their intended effects due to individual variability. As a result, many existing therapies fail to achieve their intended effects due to individual variability. Precision medicine aims to allow tailor prevention and treatment with an individual approach. (\citeprocitem{12}{Ravizza et al., 2019}). Due to the complexity of human biology, individualized medicine requires taking into account aspects that go well beyond standard medical care. Medical care only has a relative contribution of 10 to 20 percent to outcomes; health-related behaviors, socioeconomic factors, and environmental aspects account for the other 80 to 90 percent (\citeprocitem{7}{Magnan \& , 2017}). Computationally, the interdependencies and correlations among these diverse contributors create formidable challenges concerning optimizing treatment effectiveness. (\citeprocitem{8}{McDermott et al., 2012})

@@

\section{AI in Precision Medicine}
\label{sec:org742e6c1}

@@

\subsection{Accelerating AI with Quantum Computing}
\label{sec:org71a1586}

Quantum computers process information in a fundamentally different way from traditional computers. Previous computer technology advancements—such as integrated circuits—enabled faster computing, but were still based on classical information processing. These computers manipulate quantum bits (qubits). These are unlike classical bits, which store information as either a 0 or 1, and they can display uniquely quantum properties, such as entanglement. As a result, it becomes possible to construct quantum algorithms that can outperform their classical counterparts which are not able to leverage quantum phenomena. (\citeprocitem{9}{Montanaro, 2016})

\begin{itemize}
\item Chemistry, machine learning/artificial intelligence (AI), optimization, or simulation tasks. Machine learning has shown potential to be enhanced by quantum computing and is symbiotically helping drive quantum advances (\citeprocitem{2}{Carleo \& Troyer, 2017})
\item Complex correlations and interdependencies among many highly interconnected elements, such as molecular structures in which many electrons interact
\item Inherent scaling limits of relevant classical algorithms. For instance, the resource requirements of classical algorithms may increase exponentially with problem size, as is the case when simulating the time evolution of quantum systems (\citeprocitem{13}{Whitfield et al., 2011}).
\end{itemize}

\subsection{Hybrid Quantum-Classical Neural Networks}
\label{sec:org086bb1c}

@@

The most computationally demanding part of gradient-based algorithms, namely, computing the fitness function and its gradient for control input, can be accomplished by the process of evolution and measurement on quantum hardware. By posing queries to and receiving answers from these devices, classical computing devices update the control parameters until an optimal control solution is found (\citeprocitem{6}{Li et al., 2017}). Using this hybrid approach gives rise to interesting areas of research that seek to leverage the principles of quantum mechanics to augment machine learning or vice-versa. Enabling us to enhance classical ML algorithms by outsourcing difficult calculations to a quantum computer.

@@

\subsection{Generative Adversarial Networks}
\label{sec:orgd77e06b}

Generative Adversarial Networks, or GANs for short, are an approach to generative modeling using deep learning methods, such as convolutional neural networks. Generative modeling is an unsupervised learning task in machine learning that involves automatically discovering and learning the regularities or patterns in input data in such a way that the model can be used to generate or output new examples that plausibly could have been drawn from the original dataset (NO\_ITEM\_DATA:pmlr-v119-choi20a)

@@

\subsubsection{MolGAN}
\label{sec:orga8067d8}

@@

\subsubsection{Qubit-efficient Quantum Molecule Generation}
\label{sec:orgb971969}

@@

\section{Prototype}
\label{sec:orgb96e059}

@@

\subsection{Image recognition (QuTorch-HG)}
\label{sec:org48e8ed4}

@@

\subsection{Quantum Accelerated Drug \& Molecule Generation (QGAN-HG)}
\label{sec:orgea9f13d}

@@

\subsection{Data}
\label{sec:org73e7280}

@@

\subsection{Tools and Hardware}
\label{sec:org42c99db}

@@

While simulated hardware produces \emph{slightly} different results to actual hardware, the margin is within 1\%. The tests below were conducted using actual IBMQ hardware, on the \verb~ibmq_lima~ quantum computer (\citeprocitem{11}{Quantum, 2021})

@@

\section{Results}
\label{sec:org211e0f6}

\subsection{Speed}
\label{sec:org999cba1}

@@

\subsection{Accuracy}
\label{sec:org0734acb}

@@

\subsection{Pricing}
\label{sec:org272e882}

@@

\section{Conclusion and Further Research}
\label{sec:org563e7f0}

@@

\section{References}
\label{sec:org0333cf7}

@@

\hypertarget{citeproc_bib_item_6}{Li, J., Yang, X., Peng, X., \& Sun, C.-P. (2017). Hybrid quantum-classical approach to quantum optimal control. \textit{Physical Review Letters}, \textit{118}(15). \url{https://doi.org/10.1103/physrevlett.118.150503}}

\hypertarget{citeproc_bib_item_7}{Magnan, S., \& . (2017). Social determinants of health 101 for health care: Five plus five. \textit{NAM Perspectives}, \textit{7}(10). \url{https://doi.org/10.31478/201710c}}

\hypertarget{citeproc_bib_item_8}{McDermott, J. E., Wang, J., Mitchell, H., Webb-Robertson, B.-J., Hafen, R., Ramey, J., \& Rodland, K. D. (2012). Challenges in biomarker discovery: combining expert insights with statistical analysis of complex omics data. \textit{Expert Opinion on Medical Diagnostics}, \textit{7}(1), 37–51. \url{https://doi.org/10.1517/17530059.2012.718329}}

\hypertarget{citeproc_bib_item_9}{Montanaro, A. (2016). Quantum algorithms: an overview. \textit{Npj Quantum Information}, \textit{2}(1). \url{https://doi.org/10.1038/npjqi.2015.23}}

\hypertarget{citeproc_bib_item_10}{NCHIT. (2021). \textit{Non-federal acute care hospital electronic health record adoption}. \url{https://www.healthit.gov/data/}}

\hypertarget{citeproc_bib_item_11}{Quantum, I. (2021). \textit{Ibm quantum services}. \url{https://quantum-computing.ibm.com/}}

\hypertarget{citeproc_bib_item_12}{Ravizza, S., Huschto, T., Adamov, A., Böhm, L., Büsser, A., Flöther, F. F., Hinzmann, R., König, H., McAhren, S. M., Robertson, D. H., Schleyer, T., Schneidinger, B., \& Petrich, W. (2019). Predicting the early risk of chronic kidney disease in patients with diabetes using real-world data. \textit{Nature Medicine}, \textit{25}(1), 57–59. \url{https://doi.org/10.1038/s41591-018-0239-8}}

\hypertarget{citeproc_bib_item_13}{Whitfield, J. D., Biamonte, J., \& Aspuru-Guzik, A. (2011). Simulation of electronic structure hamiltonians using quantum computers. \textit{Molecular Physics}, \textit{109}(5), 735–750. \url{https://doi.org/10.1080/00268976.2011.552441}}

NO\_ITEM\_DATA:pmlr-v119-choi20a
\end{hangparas}
